Run AwAI: StarCraftII Adversary Avoidance Using Neural Networks and Genetic Algorithms

### 2018-06-01 paper.tex
added blurb on pysc2 interface
Added a section on map variations and learning environments

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{chart}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Control and data flow through the Run AwAI controller.}
\end{changemargin}
\end{figure}

@@

\subsection{PySC2 Agent Interface}

>>>>

\begin{figure}[H]
\centering
%\includegraphics[width=0.45\textwidth]{chart}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Control and data flow through the Run AwAI controller.}
\end{changemargin}
\end{figure}

@@

\subsection{PySC2 Interface}

The learning environment was based on the existing mini game environments from the PySC2 API. Specifically, our learning environment was built on top of the DefeatRoaches mini game.

The maps were retrieved from Deepmind's PySC2 Github repository and 
put into the StarcraftII/Maps/ directory.

All maps were edited in the SCII map editor.

\subsubsection{Learning Environment}
The DefeatRoaches mini game is 64x64 simple map without any obstacles that spawns a group of marines and roaches at two spawn points within the map.

\subsubsection{Map Variations}
DefeatRoaches 1v1 - 
Similar to the DefeatRoaches map except for the number of marines and 
roaches in the map at spawn time. This custom map only has 1 marine and 1 roach at the designated spawn points.

The decision to make this custom map was made early on to make the learning environment as simple as possible for training purposes.

DefeatRoaches96 - 
This variation, DefeatRoaches96, is a 96x96 map that is bigger than the original. This allows the agent to have a larger input space to choose from which could potentially improve rate of convergence.
